---
title: "Dictionary"
author: "Joschka Schwarz"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: show
---

<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: #2DC6D6;
}
</style>

# Helpful code chunks
## General bits

1. `?function_name`
This function provides information about how particular pieces of syntax work. 

```{r, eval=FALSE}
?list.files
```

2. `list.files()`
This function lists all the names of each file in a given R project.
```{r}
list.files()
```

...

***

## Input and output
1. `saveRDS()`
This saves an R object to a file.
```{r}
x <- 1
saveRDS("x", file = "testfile.rds")
```


2. `readRDS()`
This loads saved data.
```{r}
x <- readRDS(file = "testfile.rds")
```

...

***

## Data Creation
1. `c()`
This function is used to combine elements (factors in a vectore for example)
```{r}
numbers <- c(1,2,3,4,5)
numbers <- c(1:5)
print(numbers)
```


2. `seq()`
Generates a sequence of numbers. The first two values are the starting and (maximal) end values of the sequence. The third is the step width of the sequence.
```{r}
seq(1,10,2)
```

3. `rep()`
This function replicates the first number the number of times that is designated in the second space
```{r}
rep(1,10)
```


4. `data.frame()`
This allows one to enter specific groups of data values
```{r}
df <- data.frame(col_A = c(1, 2, 3, 5), col_B = c("A", "B", "C", "D"))
df
```

5. ...

## Slicing and extracting data indexing vectors

* `x[n]` nth element
* `x[-n]` all but nth element
* `x[1:n]` first n elements
* `x[-(1:n)]` elements from n+1 to the end
* `x[c(1,4,2)]` specific elements
* `x[“name”]` elements named “name”
* `x[x>3]` all elements greater than 3
* `x[x > 3 & x < 5]` all elements between 3 and 5
* `x[x %in% c(“a”,“and”,“the”)]` all elements in given set

## Indexing lists

* `x[n]` list with elements n
* `x[[n]]` nth element of the list
* `x[[“name”]]` element of the list named “name”. Alternatively: `x$name`

## Indexing matrices

* x[i,j] element at row i, column j
* x[i,] row i
* x[,j] column j
* x[,c(1,3)] columns 1 and 3
* x[“name”,] row named “name”

## Indexing data frames 

Matrix indexing plus the following

* x[[“name”]] column named “name”. Alternatively: `x$name`


## Variable conversion

as.data.frame(x)
as.numeric(x)
as.logical(x)
as.character(x)

## Variable information

1. `is.na(x)`
2. `is.null(x)`
3. `is.data.frame(x)`
4. `is.numeric(x)`
5. `is.character(x)`
6. `length(x)`
7. `dim(x)`
9. `nrow(x)`
10. `ncol(x)`
11. `class()`
12. `attributes()`

## Data selection and manipulation

1. `which.max()`
2. `which.min()`
3. `which()`
4. `sort()`
5. `unique()`
6. `table()`
7. `sample()`

## Math

1. `max()`

This sets the maximum value included in a data set.
```{r}
x <- c(1,2,3,4,5,10)
max(x)
```

2. `min()`

This set the minimum value included in a data set.
```{r}
x <- c(1,10,20,100)
min(x)
```


3. `range()`

This determines the range of numbers considered in a set.
```{r}
x <- c(1, 10, 20, 40, 100)
range(x)
```


4. `sum()`

This function adds all the numbers in a given set.
```{r}
x <- c(1, 10, 20, 40, 100)
sum(x)

```


5. `mean()`

Creates the mean of a given set of number values.
```{r}
x <- c(1, 10, 20, 40, 100)
mean(x)
```


6. `median()`

calculates the median of a set of numbers.
```{r}
x <- c(1, 10, 20, 40,  100)
median(x)
```


7. `var()`

This calculates the variance of a set of values.
```{r}
x <- c(1, 10, 20, 40, 100)
var(x)
```

8. `sd()`

This calculates the standard deviation of a set of values.
```{r}
x <- c(1, 10, 20, 40, 100)
sd(x)
```

9. `cor()`

This calculates the correlation between groups of data.
```{r}
x <- c(1, 10, 20, 40, 100)
y <- c(50, 60, 100, 200, 300)
cor(x,y)
```

10. `round()`

This rounds a decimal to a specified number of decimals.
```{r}
round(5.4567,1)
```

11. `abs()`

This takes the absolute value of a given number.
```{r}
abs(-20)
```


## Matrices

* `t()`
* `diag()`
* `rowSums()`
* `colSums()`
* `rowMeans()`
* `colMeans()`

## Advanced Data processing

* `lapply()`
* `aggregate()`

## Strings

* `paste()`
* `strsplit()`
* `tolower()`
* `toupper()`

## Plotting

* `hist()`

This function creates a histogram graph of a given set of data.
```{r}
x <- c(1,20,50)
hist(x)
```

* `plot()`

This function creates a plot graph of a given set of data.
```{r}
x <- cbind(c(1,2,3,4),c(10,20,30,40))
plot(x)
```


## Distributions

* `rnorm()`

This function inserts a normal distribution.
```{r, eval=F}
rnorm(100, mean = 50, sd=2)
```

Because of `eval=F`, the code will not be evaluated in the last piece of code.
