---
title: "Journal (reproducible report)"
author: "Osaiyekemwen Agbonaye"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# My first post

Last compiled: `r Sys.Date()`

Notice that whatever you define as a top level header, automatically gets put into the table of contents bar on the left. 

## Second level header

You can add more headers by adding more hashtags. These won't be put into the table of contents

### third level header

Here's an even lower level header

# My second post (note the order)

Last compiled: `r Sys.Date()`

I'm writing this tutorial going from the top down. And, this is how it will be printed. So, notice the second post is second in the list. If you want your most recent post to be at the top, then make a new post starting at the top. If you want the oldest first, do, then keep adding to the bottom

# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r plot, fig.width=10, fig.height=7}
#Run libraries

#libraries
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readxl)
library(readr)
library(lubridate)
library("writexl")
library(genius)
library(spotifyr)
library(plotly)
library(ggplot2)
library(rvest)
library(xopen)
library(jsonlite)
library(glue)
library(stringi)
library(furrr)
library(RSQLite)
library(httr)
library(keyring)
library(rstudioapi)
library(stringr)
library(purrr)
#Importing the files

bikes_tbl <- read_excel(path = "DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel(path = "DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl <- read_excel(path = "DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")
#run data wrangling 
glimpse(bike_orderlines_joined_tbl)
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))

bike_orderlines_joined_tbl %>% 
  select(category) %>%
  filter(str_detect(category, "^road")) %>% 
  unique()

bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  separate(col = category,
           into = c("category.1", "category.2", "category.3"),
           sep = " - ")%>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>%
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))

bike_orderlines_wrangled_2_tbl <- bike_orderlines_wrangled_tbl %>%
  separate(col = location,
           into = c("city", "state"),
           sep = ", ")%>%
  select(order_id, contains("order"), contains("model"), contains("category"),
         price, quantity, total_price,
         everything())

#first solution for state 

sales_by_state_tbl <- bike_orderlines_wrangled_2_tbl %>%
  select(state, total_price) %>%
  group_by(state) %>%
  summarize(sales = sum(total_price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".",
                                     decimal.mark = ",",
                                     prefix = "",
                                     suffix = " \U20AC"))
sales_by_state_tbl %>%
  ggplot(aes(x=state, y=sales))+
  geom_col(fill = "#FFDB6D")+
  geom_label(aes(label=sales_text))+
  geom_smooth(method="lm", se=FALSE)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".",
                                                    decimal.mark = ",",
                                                    prefix = "",
                                                    suffix = " \U20AC"))+
  labs(
    title = "Revenue by state",
    subtitle = "Upward Trend",
    x = "",
    y = "Revenue"
  )
#second solution price 
glimpse(bike_orderlines_wrangled_2_tbl)

sales_by_state_year_tbl <- bike_orderlines_wrangled_2_tbl %>%
  select(order_date, total_price, state) %>%
  mutate(year = year(order_date)) %>%
  group_by(year, state) %>%
  summarize(sales = sum(total_price)) %>%
  #theme(axis.text.x = element_text(angle = 45, hjust = 1))%>%
  ungroup()%>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".",
                                     decimal.mark = ",",
                                     prefix = "",
                                     suffix = " \U20AC"))

sales_by_state_year_tbl %>%
  ggplot(aes(x=year, y=sales, fill = state))+
  geom_col()+
  facet_wrap(~ state)+
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".",
                                                    decimal.mark = ",",
                                                    prefix = "",
                                                    suffix = " \U20AC"))+
  labs(
    title = "Revenue by Year and  the State",
    subtitle = "upward trend",
    fill = "States"
  )
#save the files
bike_orderlines_wrangled_tbl %>%
  write_xlsx("DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines.xlsx")
bike_orderlines_wrangled_tbl %>%
  write_xlsx("DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines.csv")
bike_orderlines_wrangled_tbl %>%
  write_xlsx("DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines.rds")

#########################
#Assignment 3
library(dplyr)
library(genius)
library(spotifyr)
library(plotly)
library(ggplot2)

id <- "355e1587681d43b9b387908de7f303df"
secret <- "d9096909cf974815af9f855efbe48445"
Sys.setenv(SPOTIFY_CLIENT_ID = id)
Sys.setenv(SPOTIFY_CLIENT_SECRET = secret)
access_token <- get_spotify_access_token

artist <- "wizkid"
artist_ID <- get_artist_audio_features(artist)$artist_id[1]

albums <- get_artist_albums(artist_ID, include_groups = c("album"), market = "NI",
                            authorization = access_token()) %>%
  mutate(num = row_number()) %>%
  select(name, release_date, total_tracks) %>%
  as_tibble()

albums

#Assignment3b
source("C:/Users/osazi/Documents/ws20-business-data-science-basics---lab-journal-osazioma/Codes.R")
artist <- "Ariana Grande"
artist_ID <- get_artist_audio_features(artist)$artist_id[1]

artist_ID
albums <- get_artist_albums(artist_ID, include_groups = c("single"),
                            authorization = access_token()) %>%
  mutate(num = row_number())%>%
  as_tibble()

albums

   
#3.2
url_home <- "https://www.rosebikes.com/bikes"
bikes_home <- url_home %>%
  read_html()

bike_family_tbl <- bikes_home %>%
  html_nodes(css = ".catalog-navigation__link")%>%
  html_attr('title') %>%
  discard(.p = ~stringr::str_detect(.x, "Sale"))%>%
  enframe(name = "position", value = "family_class") %>%
  mutate(family_id = str_glue("#{family_class}"))%>%
  mutate(url = glue("https://www.rosebikes.com/bikes/{family_class}"))

#bike_category_url <- bike_family_tbl$url[1]
#html_bike_category <- read_html(bike_category_url)

get_bike_data <- function(url){
 
  html_bike_category <- read_html(url)
  #bike_category_url <- bike_family_tbl$url[1]
  #html_bike_category <- read_html(bike_category_url)
 
  #urls
  bike_url_tbl <- html_bike_category %>%
    html_nodes(css =".catalog-category-bikes__button") %>%
    html_attr("href") %>%
    str_remove(pattern = "\\?.*") %>%
    enframe(name = "position",value = "part_url") %>%
    mutate(url = glue("https://www.rosebikes.com{part_url}"))
 
  #Bike Names
  bike_name_tbl <- html_bike_category %>%
    html_nodes(".catalog-category-bikes__title-text") %>%
    html_text() %>%
    str_remove(pattern = "\\n") %>%
    str_remove(pattern = "\"") %>%
    enframe(name = "position", value = "Name")
 
  #descriptions
  bike_desc_tbl <- html_bike_category %>%
    html_nodes(".catalog-category-bikes__subtitle") %>%
    html_text() %>%
    str_remove(pattern = "\\n") %>%
    str_remove(pattern = "\"") %>%
    enframe(name = "position", value = "Description")
 
  #prices
  bike_price_tbl <- html_bike_category %>%
    html_nodes(".catalog-category-bikes__price-title") %>%
    html_text() %>%
    str_remove(pattern = "\\n") %>%
    str_remove(pattern = "\"") %>%
    enframe(name = "position", value = "Price") %>%
    left_join(bike_desc_tbl, by = character()) %>%
    left_join(bike_name_tbl, by = character()) %>%
    left_join(bike_url_tbl, by = character()) %>%
    select(Name, url, Description, Price) %>%
    as_tibble()
}
rose_bike_data_tbl <- tibble()
for(i in seq_along(bike_family_tbl$url)){
  bike_category_url <- bike_family_tbl$url[i]
  rose_bike_data_tbl <- bind_rows(rose_bike_data_tbl, get_bike_data(bike_category_url))
  Sys.sleep(5)
  #print(i)
}

print(rose_bike_data_tbl, n=20)
#glimpse(rose_bike_data_tbl)
#saveRDS(rose_bike_data_tbl, "DS_101/00_data/rose_bike_data_tbl.rds")

#samples <- rnorm(100, mean=0, sd=1)
#hist(samples)

```
```{r exercise-4, include = TRUE, eval=FALSE, echo=TRUE}
knitr::opts_chunk$set(eval = FALSE)

library(tidyverse)
library(vroom)
library(data.table)
library(furrr)
library(tictoc)
library(readxl)
library(readr)
library(ggplot2)
library(dplyr)

assignee_col_types <- list(
  id = col_character(),
  type = col_character(),
  name_first = col_character(),
  name_last = col_character(),
  organization = col_character()
)

assignee_tbl <- vroom(
  file       = "exercise 4/assignee.tsv", 
  delim      = "\t", 
  col_types  = assignee_col_types,
  na         = c("", "NA", "NULL")
)

assignee_clean_tbl <- assignee_tbl %>%
  as_tibble() %>%
  rename(assignee_id = id) %>%
  select(assignee_id, type, organization)

setDT(assignee_clean_tbl)
class(assignee_clean_tbl)

patent_assignee_col_types <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_character()
)

patent_assignee_tbl <- vroom(
  file       = "exercise 4/patent_assignee.tsv", 
  delim      = "\t", 
  col_types  = patent_assignee_col_types,
  na         = c("", "NA", "NULL")
)


patent_assignee_clean_tbl <- patent_assignee_tbl %>%
  as_tibble() %>%
  select(assignee_id, patent_id)

setDT(patent_assignee_clean_tbl)
class(patent_assignee_clean_tbl)


combined_data_1_tbl <- merge(x = patent_assignee_clean_tbl, y = assignee_clean_tbl, 
                             by    = "assignee_id", 
                             all.x = TRUE, 
                             all.y = FALSE)


combined_data_1_cleaned_tbl <- combined_data_1_tbl %>%
  select(patent_id, type, organization)

saveRDS(combined_data_1_cleaned_tbl, "exercise 4/patent_1_cleaned_data_tbl.rds")

uspc_col_types <- list(
  uuid = col_character(),
  patent_id = col_character(),
  mainclass_id = col_character(),
  subclass_id = col_character(),
  sequence = col_character()
)


uspc_tbl <- vroom(
  file       = "exercise 4/uspc.tsv", 
  delim      = "\t", 
  col_types  = uspc_col_types,
  na         = c("", "NA", "NULL")
)


uspc_clean_tbl <- uspc_tbl %>%
  as_tibble() %>%
  select(patent_id, mainclass_id)

setDT(uspc_clean_tbl)
class(uspc_clean_tbl)



combined_data_2_tbl <- merge(x = uspc_clean_tbl, y = combined_data_1_cleaned_tbl, 
                             by    = "patent_id", 
                             all.x = TRUE, 
                             all.y = FALSE)

combined_data_2_cleaned_tbl <- combined_data_2_tbl %>%
  select(patent_id, type, organization,mainclass_id)

saveRDS(combined_data_2_cleaned_tbl, "exercise 4/patent_2_cleaned_data_tbl.rds")

col_types <- list(
  id = col_character(),
  type = col_character(),
  number = col_character(),
  country = col_character(),
  date = col_date("%Y-%m-%d"),
  abstract = col_character(),
  title = col_character(),
  kind = col_character(),
  num_claims = col_double(),
  filename = col_character(),
  withdrawn = col_double()
)

patent_tbl <- vroom(
  file       = "exercise 4/patent.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

patent_clean_tbl <- patent_tbl %>%
  as_tibble() %>%
  rename(patent_id = id) %>%
  select(patent_id, date)

setDT(patent_clean_tbl)
class(patent_clean_tbl)


combined_data_3_tbl <- merge(x = patent_clean_tbl, y = combined_data_2_cleaned_tbl, 
                             by    = "patent_id", 
                             all.x = TRUE, 
                             all.y = FALSE)


combined_data_3_cleaned_tbl <- combined_data_3_tbl %>%
  select(patent_id, type, date, organization, mainclass_id)


saveRDS(combined_data_3_cleaned_tbl, "exercise 4/patent_3_cleaned_data_tbl.rds")


assignee_pa_p_uspc_data <- readRDS("exercise 4/patent_3_cleaned_data_tbl.rds")

assignee_pa_p_uspc_data_tbl <- as.data.table(assignee_pa_p_uspc_data)


clean_try <- assignee_pa_p_uspc_data[,year := lubridate::year(date)]
saveRDS(clean_try, "exercise 4/patent_3_cleaned_data_with_year_tbl.rds")

#combination of assignee and patent_assignee datasets
assignee_pa_data <- readRDS("exercise 4/patent_1_cleaned_data_tbl.rds")
assignee_pa_data_tbl <- as.data.table(assignee_pa_data)
assignee_pa <- assignee_pa_data_tbl[, .(COUNT = uniqueN(patent_id)), by = organization][order(-COUNT)]
assignee_pa_clean <- assignee_pa[-c(4)]
assignment_1_result <- head(assignee_pa_clean, 10)
view(assignment_1_result)
saveRDS(assignment_1_result, "exercise 4/result_1.rds")



#combination of assignee, patent_assignee, patent, and uspc datasets

assignee_pa_p_uspc_with_year_data <- readRDS("exercise 4/patent_3_cleaned_data_with_year_tbl.rds")
assignee_pa_p_uspc_data_with_year_tbl <- as.data.table(assignee_pa_p_uspc_with_year_data)
glimpse(assignee_pa_p_uspc_data_with_year_tbl)
assignee_pa_p_uspc_final_tbl <- assignee_pa_p_uspc_data_with_year_tbl[year == "2019", .(COUNT = uniqueN(patent_id)), by = organization][order(-COUNT)]
assignee_pa_p_uspc_final_tbl
assignee_pa_p_uspc_final_tbl_clean <- assignee_pa_p_uspc_final_tbl[-c(1)]
assignment_2_result <- head(assignee_pa_p_uspc_final_tbl_clean, 10)
assignment_2_result
saveRDS(assignment_2_result, "exercise 4/result_2.rds")



#combination of assignee, patent_assignee, and uspc datasets
assignee_pa_uspc_data <- readRDS("exercise 4/patent_2_cleaned_data_tbl.rds")
assignee_pa_uspc_data_tbl <- as.data.table(assignee_pa_uspc_data)
glimpse(assignee_pa_uspc_data_tbl)
assignee_pa_uspc_final_tbl <- assignee_pa_uspc_data_tbl[, .(COUNT = uniqueN(patent_id)), by = .(organization, type)][order(-COUNT)]


assignee_pa_uspc_clean <- assignee_pa_uspc_final_tbl[-c(1)]
assignment_3a_result <- head(assignee_pa_uspc_clean, 10)
assignment_3a_result
saveRDS(assignment_3a_result, "exercise 4/result_3_1.rds")


assignee_pa_uspc_final_3b_tbl <- assignee_pa_uspc_data_tbl[, .(COUNT = .N), by = type][order(-COUNT)]
assignee_pa_uspc_3b_clean <- assignee_pa_uspc_final_3b_tbl[-c(3)]
assignment_3b_result <- head(assignee_pa_uspc_3b_clean, 5)
assignment_3b_result$patent_type <- c("US Company or Corporation", "Foreign Company or Corporation", "US  Federal Government", "US Individual", "Foreign Individual")
assignment_3b_result
saveRDS(assignment_3b_result, "exercise 4/result_3_2.rds")

```

```{r result_4}

#View Results for Challenge 4 here

#List the 10 US companies with the most assigned/granted patents
result_1<- readRDS("exercise 4/result_1.rds")
print(result_1)

#List the top 10 companies with the most new granted patents for 2019
result_2 <- readRDS("exercise 4/result_2.rds")
print(result_2)

#What is the most innovative tech sector? For the top 10 companies (worldwide) with the most patents
result_3_1 <- readRDS("exercise 4/result_3_1.rds")
print(result_3_1)

#Top 5 USPTO tech main classes
result_3_2 <- readRDS("exercise 4/result_3_2.rds")
print(result_3_2)


```






When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.



